# Imputation of Non-Livestock Commodities

**Author: Josh Browning, Michael C. J. Kao**

**Description:**

This module imputes the triplet (input, productivity and output) for a given
non-livestock commodity. Instead of writing directly back to the databse,
the module saves the imputed dataset to the Statistical Working System
shared drive. The imputed values can then be loaded and saved back to the
database in the "Fill Livestock" module.

**Inputs:**

* Production domain
* Livestock Element Mapping Table
* Identity Formula Table

**Flag Changes:**

No flag change as the data is not saved back.

---
## Initialisation

load the libraries

```{r }
suppressMessages({
    library(faosws)
    library(faoswsUtil)
    library(faoswsFlag)
    library(faoswsImputation)
    library(faoswsProduction)
    library(faoswsProcessing)
    library(faoswsEnsure)
    library(magrittr)
    library(dplyr)
})
```

set up for the test environment and parameters

```{r }
R_SWS_SHARE_PATH = Sys.getenv("R_SWS_SHARE_PATH")
savePath = paste0(R_SWS_SHARE_PATH, "/kao/production/imputation_fit/")
```

This return FALSE if on the Statistical Working System

```{r }
if(CheckDebug()){

    library(faoswsModules)
    SETTINGS = ReadSettings("sws.yml")

    ## If you're not on the system, your settings will overwrite any others
    R_SWS_SHARE_PATH = SETTINGS[["share"]]

    ## Define where your certificates are stored
    SetClientFiles(SETTINGS[["certdir"]])

    ## Get session information from SWS. Token must be obtained from web interface
    GetTestEnvironment(baseUrl = SETTINGS[["server"]],
                       token = SETTINGS[["token"]])

    savePath = SETTINGS[["save_imputation_path"]]

}
```

Get user specified imputation selection

```{r }
imputationSelection = swsContext.computationParams$imputation_selection
sessionKey = swsContext.datasets[[1]]
datasetConfig = GetDatasetConfig(domainCode = sessionKey@domain,
                                 datasetCode = sessionKey@dataset)
```

Select the item list based on user input parameter

```{r }
if(!imputationSelection %in% c("session", "all"))
    stop("Incorrect imputation selection specified")
```

Build processing parameters

```{r }
processingParameters =
    productionProcessingParameters(datasetConfig = datasetConfig)
```

Get the full imputation Datakey

```{r }
completeImputationKey = getCompleteImputationKey("production")
```

NOTE (Michael): Since the animal/meat are currently imputed by the
                imputed_slaughtered and synchronise slaughtered module, so
                they should not be imputed here.

TODO (Michael): Merge the this module with the imputed slaughtered and
                synchronise slaughtered as the logic are identical.

```{r }
liveStockItems =
    getAnimalMeatMapping(R_SWS_SHARE_PATH = R_SWS_SHARE_PATH,
                         onlyMeatChildren = FALSE) %>%
    select(measuredItemParentCPC, measuredItemChildCPC) %>%
    unlist(x = ., use.names = FALSE) %>%
    unique(x = .)
```

This is the complete list of items that are in the imputation list

```{r }
nonLivestockImputationItems =
    getQueryKey("measuredItemCPC", completeImputationKey) %>%
    setdiff(., liveStockItems)
```

These are the items selected by the users

```{r }
sessionItems =
    getQueryKey("measuredItemCPC", sessionKey) %>%
    intersect(., nonLivestockImputationItems)
```

Select the commodities based on the user input parameter

```{r }
selectedItemCode =
    switch(imputationSelection,
           "session" = sessionItems,
           "all" = nonLivestockImputationItems)
```

---
## Perform Imputation
Loop through the commodities to impute the items individually.

```{r }
for(iter in seq(selectedItemCode)){
    currentItem = selectedItemCode[iter]

    ## Obtain the formula and remove indigenous and biological meat.
    ##
    ## NOTE (Michael): Biological and indigenous meat are currently removed, as
    ##                 they have incorrect data specification. They should be
    ##                 separate item with different item code rather than under
    ##                 different element under the meat code.
    formulaTable =
        getYieldFormula(itemCode = currentItem) %>%
        removeIndigenousBiologicalMeat(formula = .)

    if(nrow(formulaTable) > 1)
        stop("Imputation should only use one formula")

    ## Create the formula parameter list
    formulaParameters =
        with(formulaTable,
             productionFormulaParameters(datasetConfig = datasetConfig,
                                         productionCode = output,
                                         areaHarvestedCode = input,
                                         yieldCode = productivity,
                                         unitConversion = unitConversion)
             )

    ## Update the item/element key according to the current commodity
    subKey = completeImputationKey
    subKey@dimensions$measuredItemCPC@keys = currentItem
    subKey@dimensions$measuredElement@keys =
        with(formulaParameters, c(productionCode, areaHarvestedCode, yieldCode))

    cat("Imputation for item: ", currentItem, " (",  iter, " out of ",
        length(selectedItemCode),")\n")


    ## Start the imputation
    ## Build imputation parameter
    imputationParameters =
        with(formulaParameters,
             getImputationParameters(productionCode = productionCode,
                                     areaHarvestedCode = areaHarvestedCode,
                                     yieldCode = yieldCode)
             )

    ## NOTE (Michael): We now impute the full triplet rather than
    ##                 just production for non-primary
    ##                 products. However, in the imputeModel
    ##                 module, only the production will be
    ##                 selected and imputed for non-primary
    ##                 products.
    ##
    ##                 Nevertheless, we hope to change this and
    ##                 impute the full triplet, for all the
    ##                 commodity. We will need to transfer and
    ##                 sync the inputs just like in the meat
    ##                 case. This will allow us to merge the two
    ##                 components.
    ##

    ## Process the data.
    processedData =
        GetData(subKey) %>%
        preProcessing(data = .) %>%
        ensureProductionInputs(data = .,
                               processingParam = processingParameters,
                               formulaParameters = formulaParameters) %>%
        denormalise(normalisedData = .,
                    denormaliseKey = "measuredElement",
                    fillEmptyRecords = TRUE) %>%
        createTriplet(data = ., formula = formulaTable) %>%
        processProductionDomain(data = .,
                                processingParameters = processingParameters,
                                formulaParameters = formulaParameters)

    ## Perform imputation
    imputed =
        imputeProductionTriplet(
            data = processedData,
            processingParameters = processingParameters,
            formulaParameters = formulaParameters,
            imputationParameters = imputationParameters) %>%
        subset(x = ., select = -ensembleVariance)


    ## Check the imputation before saving.
    imputed %>%
        mutate(timePointYears = as.character(timePointYears)) %>%
        ensureProductionOutputs(data = .,
                                processingParameters = processingParameters,
                                formulaParameters = formulaParameters,
                                normalised = FALSE) %>%
        normalise(.) %>%
        filter(., flagMethod == "i" |
                  (flagObservationStatus == "I" &
                   flagMethod == "e")) %>%
        ensureProtectedData(data = .,
                            domain = sessionKey@domain,
                            dataset = sessionKey@dataset) %>%
        postProcessing(data = .) %>%
        SaveData(domain = sessionKey@domain,
                 dataset = sessionKey@dataset,
                 data = .)

}
```

---
## Return Message

```{r }
message("Imputation Completed Successfully")
```

